Binning Strategies and Related Loss for Large Data

### 2015-03-02 Paper.Rnw
Changes to loss source description

Loss of information occurs on multiple levels during the binning and rendering process. We distinguish three sources:
\begin{itemize}

\item {\it Numerical Loss}, $L^\text{N}$, occurs when points in the data set are reduced to a single points at the bin means.  Allocating points to the numerical center, or the mean of the data corresponding to that bin, causes a loss of information about the exact location of the points.

>>>>

\ktm{Loss of information occurs during the binning and rendering process. For the remainder of the paper we will assume that we are using colors in binned scatterplots to represent frequencies.  We distinguish two sources of loss in the construction of a binned scatterplot:
\begin{itemize}
\item {\it Spatial Loss}, $L^\text{S}$, occurs when points ($x_i$,$y_i$) in the data set are reduced to a single points at the bin centers ($x_l^\ast$,$y_l^\ast$). By displaying frequency information using tiles that are visually centered at the bin centers causes a loss of information about the exact location of the points.

\item {\it Frequency Loss}, $L^\text{F}$, occurs when frequency information is not rendered accurately. If a discrete color scale is used to display bin counts, then entire ranges of counts will be mapped to the same color; thus lossing precision in the display of frequencies.
\end{itemize}

Note that even though these losses may turn out to be substantial, it is, in fact, a huge gain with respect to the original scatterplot, where information is masked in large data situations due to over-plotting of points. 
}

\ktm{The following \textit{numerical, visual and freq} loss descriptions are from the old list and will be removed: }
\begin{itemize}
\item {\it Numerical Loss}, $L^\text{N}$, occurs when points in the data set are reduced to a single points at the bin means.  Allocating points to the numerical center, or the mean of the data corresponding to that bin, causes a loss of information about the exact location of the points.
